You Actually Look Twice At it (YALTAi): using an object detection approach instead of region segmentation within the Kraken engine

### 2022-07-13 article.tex
Small corrections

With the specific purpose of training models on small datasets and document text extraction, we propose to approach the document segmentation as an object detection task, following the bounding box approach of ICDAR2017 instead of the polygon detection of ICDAR2011 or the pixel categorization of HBA or HisDoc-Layout-Comp. In this context, we propose two new datasets, a historical tabular document dataset (YALTAi-Tables) and a manuscripts and early printed book dataset (YALTAi-MSS-EPB). We do not propose a specific model but instead reuse 5\textsuperscript{th} version of You Only Look Once (YOLOv5)'s tools and models. Results show up to 100 times better results on column detection for tabular documents as well as double the score of main body document detection. As YOLOv5 base version is limited to ``straight'' boxes, it limits the application to lightly or unskewed documents. Bounding box can also overlap easily and we lose the precision of polygons.

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{l|rrr|r|rr}
    \hline
                              &   Train &   Dev &   Test &   Total &   Average area &   Median area \\
    \hline
     DropCapitalZone          &    1537 &   180 &    222 &    1939 &           0.45 &          0.26 \\
     MainZone                 &    1408 &   253 &    258 &    1919 &          28.86 &         26.43 \\
     NumberingZone            &     421 &    57 &     76 &     554 &           0.18 &          0.14 \\
     MarginTextZone           &     396 &    59 &     49 &     504 &           1.19 &          0.52 \\
     GraphicZone              &     289 &    54 &     50 &     393 &           8.56 &          4.31 \\
     MusicZone                &     237 &    71 &      0 &     308 &           1.22 &          1.09 \\
     RunningTitleZone         &     137 &    25 &     18 &     180 &           0.95 &          0.84 \\
     QuireMarksZone           &      65 &    18 &      9 &      92 &           0.25 &          0.21 \\
     StampZone                &      85 &     5 &      1 &      91 &           1.69 &          1.14 \\
     DigitizationArtefactZone &       1 &     0 &     32 &      33 &           2.89 &          2.79 \\
     DamageZone               &       6 &     1 &     14 &      21 &           1.50 &          0.02 \\
     TitlePageZone            &       4 &     0 &      1 &       5 &          48.27 &         63.39 \\
    \hline
    \end{tabular}
    \caption{Caption}
    \label{tab:comp:segmonto}
\end{table}

@@

This work was made possible through the funding of the DIM MAP, now DRIM PAMIR.

>>>>

With the specific purpose of training models on small datasets and document text extraction, we propose to approach the document segmentation as an object detection task, following the bounding box approach of ICDAR2017 instead of the polygon detection of ICDAR2011 or the pixel categorization of HBA or HisDoc-Layout-Comp. In this context, we propose two new datasets, a historical tabular document dataset (YALTAi-Tables \citep{clerice_thibault_2022_6827706}) and a manuscripts and early printed book dataset (YALTAi-MSS-EPB \citep{clerice2022yaltaimss}). We do not propose a specific model but instead reuse 5\textsuperscript{th} version of You Only Look Once (YOLOv5)'s tools and models. Results show up to 100 times better results on column detection for tabular documents as well as double the score of main body document detection. As YOLOv5 base version is limited to ``straight'' boxes, it limits the application to lightly or unskewed documents. Bounding box can also overlap easily and we lose the precision of polygons.

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{l|rrr|r|rr}
    \hline
                              &   Train &   Dev &   Test &   Total &   Average area &   Median area \\
    \hline
     DropCapitalZone          &    1537 &   180 &    222 &    1939 &           0.45 &          0.26 \\
     MainZone                 &    1408 &   253 &    258 &    1919 &          28.86 &         26.43 \\
     NumberingZone            &     421 &    57 &     76 &     554 &           0.18 &          0.14 \\
     MarginTextZone           &     396 &    59 &     49 &     504 &           1.19 &          0.52 \\
     GraphicZone              &     289 &    54 &     50 &     393 &           8.56 &          4.31 \\
     MusicZone                &     237 &    71 &      0 &     308 &           1.22 &          1.09 \\
     RunningTitleZone         &     137 &    25 &     18 &     180 &           0.95 &          0.84 \\
     QuireMarksZone           &      65 &    18 &      9 &      92 &           0.25 &          0.21 \\
     StampZone                &      85 &     5 &      1 &      91 &           1.69 &          1.14 \\
     DigitizationArtefactZone &       1 &     0 &     32 &      33 &           2.89 &          2.79 \\
     DamageZone               &       6 &     1 &     14 &      21 &           1.50 &          0.02 \\
     TitlePageZone            &       4 &     0 &      1 &       5 &          48.27 &         63.39 \\
    \hline
    \end{tabular}
    \caption{Distribution of objects instances across datasets splits after random shuffling of pages for the YALTAi-MSS-EPB dataset.}
    \label{tab:comp:segmonto}
\end{table}

@@

This work was made possible through the funding of the DIM MAP, now called DRIM PAMIR.
